A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-12-01 02_Materials_and_Methods.Rmd
more about methodology

To test for correlation between the distances based on the variables *burial type* and *burial construction*, the timeframe of interest was devided into sections of 200 years. For each section of each the two variables, a matrix of the mean SED over time was calculated. The two matrizes of each section can be tested for correlation with the Mantel test, which **TODO**. The mean correlation for each of the $\frac{8*8}{2}-\frac{8}{2}=28$ region-region relations can be plotted in the *burial type*SED-*burial construction*SED space (Figure **TODO**).

@@

>>>>

To test for correlation between the distances based on the variables *burial type* and *burial construction*, the timeframe of interest was devided into sections of 200 years. For each section of each the two variables, a matrix of the mean SED over time was calculated. The two matrizes of each section can be tested for correlation with the Mantel test, which **TODO** [@mantelDetectionDiseaseClustering1967]. Since both distances compared here, *burial type* and *burial construction* distance, are interval (**?**) scale variables, the Pearson correlation coefficient [@pearsonNotesRegressionInheritance1895] can be applied as a base measure for the Mantel test. The mean correlation for each of the $\frac{8*8}{2}-\frac{8}{2}=28$ region-region relations can be plotted in the *burial type*SED-*burial construction*SED space (Figure **TODO**).

@@

The Mantel test has to be applied with Spearman's rank correlation coefficient [@spearmanProofMeasurementAssociation1904] because of the difference in the level of measurement of cultural and spatial distance.
